Mega-analysis of the Interoceptive Accuracy Scale (IAS)

### 2025-07-06 analysis/Study1.qmd
update

```{r}
load("../data/Gaggero2021/data.rda")
df2 <- data |> 
  mutate(Gender = as.character(gender)) |> 
  mutate(across(starts_with("IAS "), as.numeric)) |>
  rename(
    Age=age, Heart = `IAS 1`, Hungry = `IAS 2`, Breathing = `IAS 3`, Thirsty = `IAS 4`,
    Urinate = `IAS 5`, Defecate = `IAS 6`, Taste = `IAS 7`, Vomit = `IAS 8`, Sneeze = `IAS 9`,
    Cough = `IAS 10`, Temp = `IAS 11`, Sex_arousal = `IAS 12`, Wind = `IAS 13`, Burp = `IAS 14`,
    Muscles = `IAS 15`, Bruise = `IAS 16`, Pain = `IAS 17`, Blood_Sugar = `IAS 18`,
    Affective_touch = `IAS 19`, Tickle = `IAS 20`, Itch = `IAS 21`)
rm(data)
```

@@

```{r}
df4 <- haven::read_sav("../data/Todd2022/CompleteData_new.sav") |>
  rename_with(\(x) str_remove(x, "IAS_"), .cols = starts_with("IAS_")) |>
  rename(
    Heart = IAS1, Hungry = IAS2, Breathing = IAS3, Thirsty = IAS4,
    Urinate = IAS5, Defecate = IAS6, Taste = IAS7, Vomit = IAS8, Sneeze = IAS9,
    Cough = IAS10, Temp = IAS11, Sex_arousal = IAS12, Wind = IAS13, Burp = IAS14,
    Muscles = IAS15, Bruise = IAS16, Pain = IAS17, Blood_Sugar = IAS18,
    Affective_touch = IAS19, Tickle = IAS20, Itch = IAS21
  )
```

@@

df5 <- df5 |>
  filter(Subj.ID %in% df5_attention$Subj.ID) |>
  select(-Subj.ID) |>
  mutate(across(everything(), as.numeric))

@@

```{r}
df7a <- haven::read_sav("../data/Brand2023/Data_Giessen.sav") |> 
  select(-COUNTRY_OTHER) |> 
  mutate_all(as.numeric) |>
  mutate(Gender = as.character(ifelse(SEX == 1, "Male", ifelse(SEX == 2, "Female", "Other")))) |> 
  rename(
    Age=AGE, Heart = IAS_01, Hungry = IAS_02, Breathing = IAS_03, Thirsty = IAS_04,
    Urinate = IAS_05, Defecate = IAS_06, Taste = IAS_07, Vomit = IAS_08, Sneeze = IAS_09,
    Cough = IAS_10, Temp = IAS_11, Sex_arousal = IAS_12, Wind = IAS_13, Burp = IAS_14,
    Muscles = IAS_15, Bruise = IAS_16, Pain = IAS_17, Blood_Sugar = IAS_18,
    Affective_touch = IAS_19, Tickle = IAS_20, Itch = IAS_21
  )

df7b <- haven::read_sav("../data/Brand2023/Data_Mainz.sav") |> 
  select(-COUNTRY_OTHER, -EDUCATION_OTHER, -Sample) |> 
  mutate_all(as.numeric) |> 
  mutate(Gender = as.character(ifelse(GENDER == 2, "Male", ifelse(GENDER == 1, "Female", "Other")))) |> 
  rename(
    Age=AGE, Heart = IAS_01, Hungry = IAS_02, Breathing = IAS_03, Thirsty = IAS_04,
    Urinate = IAS_05, Defecate = IAS_06, Taste = IAS_07, Vomit = IAS_08, Sneeze = IAS_09,
    Cough = IAS_10, Temp = IAS_11, Sex_arousal = IAS_12, Wind = IAS_13, Burp = IAS_14,
    Muscles = IAS_15, Bruise = IAS_16, Pain = IAS_17, Blood_Sugar = IAS_18,
    Affective_touch = IAS_19, Tickle = IAS_20, Itch = IAS_21
  )

df7c <- haven::read_sav("../data/Brand2023/Data_PotVie.sav") |> 
  select(-ID) |> 
  mutate_all(as.numeric) |>
  mutate(Gender = as.character(ifelse(GENDER == 2, "Male", ifelse(GENDER == 1, "Female", "Other")))) |> 
  rename(
    Age=AGE, Heart = IA02_01, Hungry = IA02_02, Breathing = IA02_03, Thirsty = IA02_04,
    Urinate = IA02_05, Defecate = IA02_06, Taste = IA02_07, Vomit = IA02_08, Sneeze = IA02_09,
    Cough = IA02_10, Temp = IA02_11, Sex_arousal = IA02_12, Wind = IA02_13, Burp = IA02_14,
    Muscles = IA02_15, Bruise = IA02_16, Pain = IA02_17, Blood_Sugar = IA02_18,
    Affective_touch = IA02_19, Tickle = IA02_20, Itch = IA02_21
  )
```

@@

- Makowski
  - Note: First sample has some missing items
  - Note: Analog scales
  - note df10c = primals data

@@

@@

@@

```{r}
pi_vars <- c("PI_Enticing", "PI_Alive", "PI_Safe", "PI_Good", "PI_Changing", 
             "PI_Hierarchical", "PI_Understandable", "PI_AboutMe", "PI_Abundant", 
             "PI_Acceptable", "PI_Beautiful", "PI_Cooperative", "PI_Funny", 
             "PI_Harmless", "PI_Improvable", "PI_Intentional", "PI_Interconnected", 
             "PI_Interesting", "PI_Just", "PI_Meaningful", "PI_NeedsMe", 
             "PI_Pleasurable", "PI_Progressing", "PI_Regenerative", "PI_Stable", 
             "PI_WorthExploring")

correlation::correlation(
  df10c[, "IAS_Total", drop = FALSE],  
  data2 = select(df10c, all_of(pi_vars)), p_adjust = "none"
) |> 
  # Formatting correlation results
  mutate(val = paste0(insight::format_value(r), format_p(p, stars_only = TRUE))) |>

  # Releveling factors for visualization
  mutate(Parameter2 = fct_relevel(Parameter2, rev(pi_vars)),
         Parameter1 = fct_relevel(Parameter1, "IAS_Total")) |>

  # Plotting the correlation matrix
  ggplot(aes(x = Parameter1, y = Parameter2)) +
  geom_tile(aes(fill = r), color = "white") +  
  geom_text(aes(label = val), size = 3) +  
  labs(title = "Correlation Matrix") +
  scale_fill_gradient2(low = "blue", high = "red", mid = "white", limit = c(-1, 1), midpoint = 0, guide = guide_colourbar(ticks = FALSE)) +  
  theme_minimal() +
  theme(
    legend.title = element_blank(),
    axis.title.x = element_blank(),
    axis.title.y = element_blank(),
    axis.text.x = element_text(hjust = 1)
  )
```

@@

@@

# Create the dataframe
table <- data.frame(
   Sample = c('Murphy et al., (2020)', '', '', 'Gaggero et al., (2021)', 'Campos et al., (2022)', 'Todd et al., (2022)', 'Arslanova et al., (2022)', 'Brand et al., (2022)', 'Brand et al., (2023)', '', '', '', 'Lin et al., (2023)', '', '', 'VonMohr et al., (2023)', 'Makowski et al., (2023a)', 'Makowski et al., (2023b)', 'Makowski et al., (2023c)', 'Poerio et al., (2024)', 'Poerio et al., unpublished', 'Total'),
  Subsample = c('', 'Sample 1', 'Sample 2', '', '', '', '', '', '', 'Sample 1', 'Sample 2', 'Sample 3', '', 'Sample 1', 'Sample 2', '', '', '', '', '','', ''),   
  Language = c('', 'English', 'English' , 'English and Italian', 'Portuguese', 'English', 'English', 'German', '', 'German', 'German', 'German', '', 'Chinese', 'Chinese', 'English', 'English', 'English', 'English', 'English', 'English',''),
  N = c('', nrow(df1a), nrow(df1b), nrow(df2), nrow(df3), nrow(df4), nrow(df5_attention), nrow(df6),'', nrow(df7a), nrow(df7b), 802,'', nrow(df8a), nrow(df8b), nrow(df9), nrow(df10a), nrow(df10b), nrow(df10c), nrow(df11a), nrow(df11b), 32214),
  'Difference' = c('','', '', '', '', '', '', '', '', '', '', '', '', 'Collapsed "Itch" and "Tingling"', 'Collapsed "Itch" and "Tingling"', '', 'Analog scales', 'Analog scales', 'Analog scales', '', '', ''),
  Age = c('', make_age(df1a$Age), make_age(df1b$Age), make_age(df2$Age), make_age(df3$Age), "48.6.6 ± 14.1*", make_age(df5_attention$Age), make_age(df6$Age),'', make_age(df7a$Age), make_age(df7b$Age), make_age(df7c$Age),'', make_age(df8a$Age), make_age(df8b$Age), make_age(df9$Age), make_age(df10a$Age), make_age(df10b$Age), make_age(df10c$Age), make_age(df11a$Age), make_age(df11b$Age), '48.6 ± 13.1'),
  Range = c('', '18-69', '18-91', '18-58', '18-72', '18-92*', '18-73', '18-78', '', '18-79', '16-81', '18-72','', '16-60', '20-60', '18-93', '18-73', '17-76','18-50', '18-57', '18-60', '17-93'),
  Female_Percentage = c('', '69.4%', '70.1%', '60.3%', '59.6%', '50%*', '46.8%', '78.7%', '', '79.5%', '77.7%', '68.9%', '', '57.0%', '56.2%', '73.2%', '50.3%', '53.0%', '76%', '74.8%', '75.9%', '71.6%'),
  Availability= c('osf.io/3m5nh', '', '', 'osf.io/5x9sg', 'osf.io/j6ef3', 'osf.io/ms354', 'osf.io/mp3cy', 'osf.io/xwz6g', 'osf.io/3f2h6', '', '', '','osf.io/3eztd','', '', 'osf.io/7p9u5', 'github.com/RealityBending/IllusionGameReliability', 'github.com/DominiqueMakowski/PHQ4R', 'github.com/RealityBending/InteroceptionPrimals', 'osf.io/49wbv', '','')
)

@@

## Descriptive

@@

p1 <- p1_data |>
  mutate(Sample = fct_relevel(Sample, "Sample 1a", "Sample 1b", "Sample 2", "Sample 3", "Sample 4", "Sample 5", "Sample 6", "Sample 7a", "Sample 7b", "Sample 7c", "Sample 8a", "Sample 8b", "Sample 9", "Sample 10a", "Sample 10b", "Sample 10c", "Sample 11a", "Sample 11b"),
         Parameter = ifelse(Parameter == "Affective_touch", "Affective touch", Parameter),
         Parameter = ifelse(Parameter == "Blood_Sugar", "Blood sugar", Parameter),
         Parameter = ifelse(Parameter == "Sex_arousal", "Sex arousal", Parameter)) |>
  # mutate(Dashed = ifelse(Parameter %in% c("Affective_touch", "Blood_Sugar", "Bruise"), TRUE, FALSE)) |> 
  ggplot(aes(x = x, y = y, color = Parameter)) +
  geom_line(aes(linetype = Parameter), linewidth = 0.7) +
  scale_color_material_d() +
  scale_linetype_manual(values = linetype) +
  theme_minimal() +
  theme(axis.text.y = element_blank(),
        plot.title = element_text(face="bold")) +
  labs(x = "Response", y = "Distribution", color = "Item", linetype = "Item") +
  facet_wrap(~Sample, scales = "free_y", nrow = 3)

ggsave("figures/Figure1.png", p1, width=12, height=7, dpi=300, bg="white")
p1
```

@@

```{r}
make_correlation <- function(df) {
  correlation::correlation(df, redundant = TRUE) |>
    correlation::cor_sort() |>
    correlation::cor_lower() |>
    mutate(val = paste0(insight::format_value(r), format_p(p, stars_only = TRUE))) |>
    mutate(Parameter2 = fct_rev(Parameter2)) |>
    ggplot(aes(x = Parameter1, y = Parameter2)) +
    geom_tile(aes(fill = r), color = "white") +
    geom_text(aes(label = val), size = 3) +
    labs(title = "Correlation Matrix") +
    scale_fill_metro_c(limit = c(0, 0.75), guide = guide_colourbar(ticks = FALSE)) +
    theme_minimal() +
    theme(
      legend.title = element_blank(),
      axis.title.x = element_blank(),
      axis.title.y = element_blank(),
      axis.text.x = element_text(angle = 45, hjust = 1)
    )
}

make_correlation(data_all)
```

@@

## Graph Analysis

Exploratory Graph Analysis (EGA) is a recently developed framework for psychometric assessment, that can be used to estimate the number of dimensions in questionnaire data using network estimation methods and community detection algorithms, and assess the stability of dimensions and items using bootstrapping.
See https://r-ega.net/articles/ega.html for details.

@@

```{r}
uva <- EGAnet::UVA(data = data_all, cut.off = 0.3)
uva
uva$keep_remove
```

@@

```{r}
uva <- EGAnet::UVA(data = data1a, cut.off = 0.3)
uva
uva$keep_remove
```

@@

```{r}
uva <- EGAnet::UVA(data = data1b, cut.off = 0.3)
uva
uva$keep_remove
```

@@

```{r}
uva <- EGAnet::UVA(data = data3, cut.off = 0.3)
uva
uva$keep_remove
```

@@

```{r}
uva <- EGAnet::UVA(data = data4, cut.off = 0.3)
uva
uva$keep_remove
```

@@

```{r}
uva <- EGAnet::UVA(data = data5, cut.off = 0.3)
uva
uva$keep_remove
```

@@

```{r}
uva <- EGAnet::UVA(data = data6, cut.off = 0.3)
uva
uva$keep_remove
```

@@

```{r}
uva <- EGAnet::UVA(data = data7a, cut.off = 0.3)
uva
uva$keep_remove
```

@@

```{r}
uva <- EGAnet::UVA(data = data7b, cut.off = 0.3)
uva
uva$keep_remove
```

@@

```{r}
uva <- EGAnet::UVA(data = data7c, cut.off = 0.3)
uva
uva$keep_remove
```

@@

```{r}
uva <- EGAnet::UVA(data = data8a, cut.off = 0.3)
uva
uva$keep_remove
```

@@

```{r}
uva <- EGAnet::UVA(data = data8b, cut.off = 0.3)
uva
uva$keep_remove
```

@@

```{r}
uva <- EGAnet::UVA(data = data9, cut.off = 0.3)
uva
uva$keep_remove
```

@@

```{r}
uva <- EGAnet::UVA(data = data10a, cut.off = 0.3)
uva
uva$keep_remove
```

@@

```{r}
uva <- EGAnet::UVA(data = data10b, cut.off = 0.3)
uva
uva$keep_remove
```

@@

```{r}
uva <- EGAnet::UVA(data = data10c, cut.off = 0.3)
uva
uva$keep_remove
```

@@

```{r}
uva <- EGAnet::UVA(data = data11a, cut.off = 0.3)
uva
uva$keep_remove
```

@@

```{r}
uva <- EGAnet::UVA(data = data11b, cut.off = 0.3)
uva
uva$keep_remove
```

@@

### Networks

>>>>

```{r}
load("../data/Gaggero2021/data.rda")
df2 <- data |> 
  mutate(Gender = as.character(gender)) |> 
  mutate(across(starts_with("IAS "), as.numeric)) |>
  rename(
    Age=age, Heart = `IAS 1`, Hungry = `IAS 2`, Breathing = `IAS 3`, Thirsty = `IAS 4`,
    Urinate = `IAS 5`, Defecate = `IAS 6`, Taste = `IAS 7`, Vomit = `IAS 8`, Sneeze = `IAS 9`,
    Cough = `IAS 10`, Temp = `IAS 11`, Sex_arousal = `IAS 12`, Wind = `IAS 13`, Burp = `IAS 14`,
    Muscles = `IAS 15`, Bruise = `IAS 16`, Pain = `IAS 17`, Blood_Sugar = `IAS 18`,
    Affective_touch = `IAS 19`, Tickle = `IAS 20`, Itch = `IAS 21`,
    MAIA_AttentionRegulation = MAIA_AttentionReg, MAIA_BodyListening = MAIA_BodyListening,
    MAIA_Trusting = MAIA_BodyTrusting, MAIA_EmotionalAwareness = MAIA_EmoAwareness,
    MAIA_NonDistracting=MAIA_NotDistracting, MAIA_NotWorrying=MAIA_NotWorrying,
    MAIA_SelfRegulation=MAIA_SelfReg, MAIA_Noticing=MAIA_Noticing)
rm(data)
```

@@

```{r}
df4 <- haven::read_sav("../data/Todd2022/CompleteData_new.sav") |>
  rename_with(\(x) str_remove(x, "IAS_"), .cols = starts_with("IAS_")) |>
  rename(
    Heart = IAS1, Hungry = IAS2, Breathing = IAS3, Thirsty = IAS4,
    Urinate = IAS5, Defecate = IAS6, Taste = IAS7, Vomit = IAS8, Sneeze = IAS9,
    Cough = IAS10, Temp = IAS11, Sex_arousal = IAS12, Wind = IAS13, Burp = IAS14,
    Muscles = IAS15, Bruise = IAS16, Pain = IAS17, Blood_Sugar = IAS18,
    Affective_touch = IAS19, Tickle = IAS20, Itch = IAS21
  )
df4$MAIA_AttentionRegulation <- rowMeans(select(df4, starts_with("MAIA_AR")), na.rm = TRUE)
df4$MAIA_BodyListening <- rowMeans(select(df4, starts_with("MAIA_BL")), na.rm = TRUE)
df4$MAIA_Trusting <- rowMeans(select(df4, starts_with("MAIA_TR")), na.rm = TRUE)
df4$MAIA_EmotionalAwareness <- rowMeans(select(df4, starts_with("MAIA_EA")), na.rm = TRUE)
df4$MAIA_SelfRegulation <- rowMeans(select(df4, starts_with("MAIA_SR")), na.rm = TRUE)
# TODO: what is NT?
# Check if that's all
```

@@

df5 <- df5 |>
  filter(Subj.ID %in% df5_attention$Subj.ID) |>
  select(-Subj.ID) |>
  mutate(across(everything(), as.numeric))
```

@@

```{r}
df7a <- haven::read_sav("../data/Brand2023/Data_Giessen.sav") |> 
  select(-COUNTRY_OTHER) |> 
  mutate_all(as.numeric) |>
  mutate(Gender = as.character(ifelse(SEX == 1, "Male", ifelse(SEX == 2, "Female", "Other")))) |> 
  rename(
    Age=AGE, Heart = IAS_01, Hungry = IAS_02, Breathing = IAS_03, Thirsty = IAS_04,
    Urinate = IAS_05, Defecate = IAS_06, Taste = IAS_07, Vomit = IAS_08, Sneeze = IAS_09,
    Cough = IAS_10, Temp = IAS_11, Sex_arousal = IAS_12, Wind = IAS_13, Burp = IAS_14,
    Muscles = IAS_15, Bruise = IAS_16, Pain = IAS_17, Blood_Sugar = IAS_18,
    Affective_touch = IAS_19, Tickle = IAS_20, Itch = IAS_21,
    MAIA_Noticing = MAIA_NOTICING, MAIA_NonDistracting = MAIA_NON_DISTRACTING,
    MAIA_NotWorrying = MAIA_NOT_WORRYING, MAIA_AttentionRegulation = mAIA_ATTENTION_REGULATION,
    MAIA_SelfRegulation = MAIA_SELF_REGULATION, MAIA_BodyListening = MAIA_BODY_LISTENING,
    MAIA_Trusting = MAIA_TRUSTING, MAIA_EmotionalAwareness = MAIA_EMOTIONAL_AWARENESS
  )

df7b <- haven::read_sav("../data/Brand2023/Data_Mainz.sav") |> 
  select(-COUNTRY_OTHER, -EDUCATION_OTHER, -Sample) |> 
  mutate_all(as.numeric) |> 
  mutate(Gender = as.character(ifelse(GENDER == 2, "Male", ifelse(GENDER == 1, "Female", "Other")))) |> 
  rename(
    Age=AGE, Heart = IAS_01, Hungry = IAS_02, Breathing = IAS_03, Thirsty = IAS_04,
    Urinate = IAS_05, Defecate = IAS_06, Taste = IAS_07, Vomit = IAS_08, Sneeze = IAS_09,
    Cough = IAS_10, Temp = IAS_11, Sex_arousal = IAS_12, Wind = IAS_13, Burp = IAS_14,
    Muscles = IAS_15, Bruise = IAS_16, Pain = IAS_17, Blood_Sugar = IAS_18,
    Affective_touch = IAS_19, Tickle = IAS_20, Itch = IAS_21,
    MAIA_Noticing = maiaNotice, MAIA_NonDistracting = maiaNonDistracting,
    MAIA_NotWorrying = maiaNotWorrying, MAIA_AttentionRegulation = maiaAttentionRegulation,
    MAIA_SelfRegulation = maiaSelfRegulation, MAIA_BodyListening = maiaBodyListening,
    MAIA_Trusting = maiaTrusting, MAIA_EmotionalAwareness = maiaEmotionalAwareness
  )

df7c <- haven::read_sav("../data/Brand2023/Data_PotVie.sav") |> 
  select(-ID) |> 
  mutate_all(as.numeric) |>
  mutate(Gender = as.character(ifelse(GENDER == 2, "Male", ifelse(GENDER == 1, "Female", "Other")))) |> 
  rename(
    Age=AGE, Heart = IA02_01, Hungry = IA02_02, Breathing = IA02_03, Thirsty = IA02_04,
    Urinate = IA02_05, Defecate = IA02_06, Taste = IA02_07, Vomit = IA02_08, Sneeze = IA02_09,
    Cough = IA02_10, Temp = IA02_11, Sex_arousal = IA02_12, Wind = IA02_13, Burp = IA02_14,
    Muscles = IA02_15, Bruise = IA02_16, Pain = IA02_17, Blood_Sugar = IA02_18,
    Affective_touch = IA02_19, Tickle = IA02_20, Itch = IA02_21,
    MAIA_Noticing = MAIA_noticing, MAIA_NonDistracting = MAIA_notdis, 
    MAIA_NotWorrying = MAIA_notwor, MAIA_AttentionRegulation = MAIA_attreg,
    MAIA_SelfRegulation = MAIA_selfreg, MAIA_BodyListening = MAIA_bodlis,
    MAIA_Trusting = MAIA_trust, MAIA_EmotionalAwareness = MAIA_emoaw,
    ICQ = ICQ_sum
  )
```

@@

- Makowski
  - Note: First sample has some missing items (No Taste, Cough, Blood_Sugar)
  - Note: Analog scales
  - note df10c = primals data

@@

# TODO: Sanitize MAIA names / Compute dimensions.

@@

# TODO: Sanitize MAIA names / Compute dimensions.

df10d <- read.csv("https://raw.githubusercontent.com/RealityBending/InteroceptionScale/refs/heads/main/study2/data/rawdata_participants.csv") |>
  select("Participant", "Gender", "Age", "Ethnicity", starts_with(c("IAS","MAIA","PI", "PHQ4"))) |>
   rename(
    Heart = IAS_1, Hungry = IAS_2, Breathing = IAS_3, Thirsty = IAS_4,
    Urinate = IAS_5, Defecate = IAS_6, Taste = IAS_7, Vomit = IAS_8, Sneeze = IAS_9,
    Cough = IAS_10, Temp = IAS_11, Sex_arousal = IAS_12, Wind = IAS_13, Burp = IAS_14,
    Muscles = IAS_15, Bruise = IAS_16, Pain = IAS_17, Blood_Sugar = IAS_18,
    Affective_touch = IAS_19, Tickle = IAS_20, Itch = IAS_21
  ) |> 
  filter(Participant %in% read.csv("https://raw.githubusercontent.com/RealityBending/InteroceptionScale/refs/heads/main/study2/data/data_participants.csv")$Participant)

# TODO: Sanitize MAIA names / Compute dimensions.

@@

```{r}
# pi_vars <- c("PI_Enticing", "PI_Alive", "PI_Safe", "PI_Good", "PI_Changing", 
#              "PI_Hierarchical", "PI_Understandable", "PI_AboutMe", "PI_Abundant", 
#              "PI_Acceptable", "PI_Beautiful", "PI_Cooperative", "PI_Funny", 
#              "PI_Harmless", "PI_Improvable", "PI_Intentional", "PI_Interconnected", 
#              "PI_Interesting", "PI_Just", "PI_Meaningful", "PI_NeedsMe", 
#              "PI_Pleasurable", "PI_Progressing", "PI_Regenerative", "PI_Stable", 
#              "PI_WorthExploring")
# 
# 
# correlation::correlation(
#   df10c[, "IAS_Total", drop = FALSE],  
#   data2 = select(df10c, all_of(pi_vars)), p_adjust = "none"
# ) |> 
#   # Formatting correlation results
#   mutate(val = paste0(insight::format_value(r), format_p(p, stars_only = TRUE))) |>
#   
#   # Releveling factors for visualization
#   mutate(Parameter2 = fct_relevel(Parameter2, rev(pi_vars)),
#          Parameter1 = fct_relevel(Parameter1, "IAS_Total")) |>
#   
#   # Plotting the correlation matrix
#   ggplot(aes(x = Parameter1, y = Parameter2)) +
#   geom_tile(aes(fill = r), color = "white") +  
#   geom_text(aes(label = val), size = 3) +  
#   labs(title = "Correlation Matrix") +
#   scale_fill_gradient2(low = "blue", high = "red", mid = "white", limit = c(-1, 1), midpoint = 0, guide = guide_colourbar(ticks = FALSE)) +  
#   theme_minimal() +
#   theme(
#     legend.title = element_blank(),
#     axis.title.x = element_blank(),
#     axis.title.y = element_blank(),
#     axis.text.x = element_text(hjust = 1)
#   )
```

@@

# TODO: sanitize MAIA names / Compute dimensions.

@@

# Create the dataframe
table <- data.frame(
  Reference = c('Murphy et al., (2020)', '', '', 'Gaggero et al., (2021)', 'Campos et al., (2022)', 'Todd et al., (2022)', 'Arslanova et al., (2022)', 'Brand et al., (2022)', 'Brand et al., (2023)', '', '', '', 'Lin et al., (2023)', '', '', 'VonMohr et al., (2023)', 'Makowski et al., (2023a)', 'Makowski et al., (2023b)', 'Makowski et al., (2023c)', 'Poerio et al., (2024)', 'Poerio et al., unpublished', 'Total'),
  Sample = c('', 'Sample 1a', 'Sample 1b', 'Sample 2', 'Sample 3', 'Sample 4', 'Sample 5', 'Sample 6', '', 'Sample 7a', 'Sample 7b', 'Sample 7c', '', 'Sample 8a', 'Sample 8b', 'Sample 9', 'Sample 10', 'Sample 11', 'Sample 12', 'Sample 13', 'Sample 14', 'Sample 15'),   
  Language = c('', 'English', 'English' , 'English and Italian', 'Portuguese', 'English', 'English', 'German', '', 'German', 'German', 'German', '', 'Chinese', 'Chinese', 'English', 'English', 'English', 'English', 'English', 'English',''),
  N = c('', nrow(df1a), nrow(df1b), nrow(df2), nrow(df3), nrow(df4), nrow(df5_attention), nrow(df6),'', nrow(df7a), nrow(df7b), 802,'', nrow(df8a), nrow(df8b), nrow(df9), nrow(df10a), nrow(df10b), nrow(df10c), nrow(df11a), nrow(df11b), 32214),
  'Difference' = c('','', '', '', '', '', '', '', '', '', '', '', '', 'Collapsed "Itch" and "Tickling"', 'Collapsed "Itch" and "Tickling"', '', 'Analog scales', 'Analog scales', 'Analog scales', '', '', ''),
  Age = c('', make_age(df1a$Age), make_age(df1b$Age), make_age(df2$Age), make_age(df3$Age), "48.6.6 ± 14.1*", make_age(df5_attention$Age), make_age(df6$Age),'', make_age(df7a$Age), make_age(df7b$Age), make_age(df7c$Age),'', make_age(df8a$Age), make_age(df8b$Age), make_age(df9$Age), make_age(df10a$Age), make_age(df10b$Age), make_age(df10c$Age), make_age(df11a$Age), make_age(df11b$Age), '48.6 ± 13.1'),
  Range = c('', '18-69', '18-91', '18-58', '18-72', '18-92*', '18-73', '18-78', '', '18-79', '16-81', '18-72','', '16-60', '20-60', '18-93', '18-73', '17-76','18-50', '18-57', '18-60', '17-93'),
  Female_Percentage = c('', '69.4%', '70.1%', '60.3%', '59.6%', '50%*', '46.8%', '78.7%', '', '79.5%', '77.7%', '68.9%', '', '57.0%', '56.2%', '73.2%', '50.3%', '53.0%', '76%', '74.8%', '75.9%', '71.6%'),
  Availability= c('osf.io/3m5nh', '', '', 'osf.io/5x9sg', 'osf.io/j6ef3', 'osf.io/ms354', 'osf.io/mp3cy', 'osf.io/xwz6g', 'osf.io/3f2h6', '', '', '','osf.io/3eztd','', '', 'osf.io/7p9u5', 'github.com/RealityBending/IllusionGameReliability', 'github.com/DominiqueMakowski/PHQ4R', 'github.com/RealityBending/InteroceptionPrimals', 'osf.io/49wbv', '','')
)

@@

## Item Selection

@@

p1 <- p1_data |>
  mutate(Sample = fct_relevel(Sample, "Sample 1a", "Sample 1b", "Sample 2", "Sample 3", "Sample 4", "Sample 5", "Sample 6", "Sample 7a", "Sample 7b", "Sample 7c", "Sample 8a", "Sample 8b", "Sample 9", "Sample 10a", "Sample 10b", "Sample 10c", "Sample 11a", "Sample 11b"),
         Parameter = ifelse(Parameter == "Affective_touch", "Affective touch", Parameter),
         Parameter = ifelse(Parameter == "Blood_Sugar", "Blood sugar", Parameter),
         Parameter = ifelse(Parameter == "Sex_arousal", "Sex arousal", Parameter)) |>
  # mutate(Dashed = ifelse(Parameter %in% c("Affective_touch", "Blood_Sugar", "Bruise"), TRUE, FALSE)) |> 
  ggplot(aes(x = x, y = y, color = Parameter)) +
  geom_line(aes(linetype = Parameter), linewidth = 0.7) +
  scale_color_material_d() +
  scale_linetype_manual(values = linetype)  +
  labs(x = "Response", y = "Distribution", color = "Item", linetype = "Item", title = "Item Distribution") +
  guides(color = guide_legend(ncol = 1)) +
  facet_wrap(~Sample, scales = "free_y", nrow = 3) +
  theme_minimal() +
  theme(axis.text.y = element_blank(),
        axis.title.y = element_blank(),
        plot.title = element_text(face="bold"))

p1
```

@@

```{r}
make_correlation <- function(df) {
  correlation::correlation(df, redundant = TRUE) |>
    correlation::cor_sort() |>
    # correlation::cor_lower() |>
    mutate(val = paste0(insight::format_value(r), format_p(p, stars_only = TRUE)),
           r = ifelse(Parameter1 == Parameter2, NA, r),
           lbl = ifelse(Parameter1 == Parameter2, "", format_value(r, zap_small = TRUE, lead_zero = FALSE)),
           lbl = ifelse(p > .05, "", lbl),
           Param1 = fct_relevel(str_replace(Parameter1, "_", " "), str_replace(levels(Parameter1), "_", " ")),
           Param2 = fct_relevel(str_replace(Parameter2, "_", " "), str_replace(levels(Parameter2), "_", " "))) |>
    # mutate(Parameter2 = fct_rev(Parameter2)) |>
    ggplot(aes(x = Param1, y = Param2)) +
    geom_tile(aes(fill = r), color = "white") +
    geom_text(aes(label = lbl), size = 3) +
    labs(title = "Correlation Matrix", subtitle = paste0("N = ", nrow(df))) +
    scale_fill_gradientn(
      colors = c("white", "#FFF9C4", "#FFF59D", "#FFEB3B", "#FFCA28", "#FF9800", "#FF5722", "#F44336", "#E91E63", "#9C27B0", "#673AB7", "#512DA8", "#311B92"),
      na.value = "#311B92",
      limits = c(0, 0.8),
      guide = guide_colorbar(ticks.colour = NA)
    ) +
    # scale_fill_metro_c(limit = c(0, 0.75), guide = guide_colourbar(ticks = FALSE)) +
    theme_minimal() +
    theme(
      legend.title = element_blank(),
      axis.title.x = element_blank(),
      axis.title.y = element_blank(),
      axis.text.x = element_text(angle = 45, hjust = 1),
      plot.title = element_text(face = "bold")
    )
}

p2 <- make_correlation(data_all)
p2

fig1 <- p1 / p2
ggsave("figures/Figure1.png", fig1, width=10, height=12, dpi=300, bg="white")
```

@@

@@

```{r}
uva0 <- EGAnet::UVA(data = data_all, cut.off = 0.3)
uva0
uva0$keep_remove
```

@@

```{r}
uva1a <- EGAnet::UVA(data = data1a, cut.off = 0.3)
uva1a
uva1a$keep_remove
```

@@

```{r}
uva1b <- EGAnet::UVA(data = data1b, cut.off = 0.3)
uva1b
uva1b$keep_remove
```

```{r}
uva2 <- EGAnet::UVA(data = data2, cut.off = 0.3)
uva2
uva2$keep_remove
```

@@

```{r}
uva3 <- EGAnet::UVA(data = data3, cut.off = 0.3)
uva3
uva3$keep_remove
```

@@

```{r}
uva4 <- EGAnet::UVA(data = data4, cut.off = 0.3)
uva4
uva4$keep_remove
```

@@

```{r}
uva5 <- EGAnet::UVA(data = data5, cut.off = 0.3)
uva5
uva5$keep_remove
```

@@

```{r}
uva6 <- EGAnet::UVA(data = data6, cut.off = 0.3)
uva6
uva6$keep_remove
```

@@

```{r}
uva7a <- EGAnet::UVA(data = data7a, cut.off = 0.3)
uva7a
uva7a$keep_remove
```

@@

```{r}
uva7b <- EGAnet::UVA(data = data7b, cut.off = 0.3)
uva7b
uva7b$keep_remove
```

@@

```{r}
uva7c <- EGAnet::UVA(data = data7c, cut.off = 0.3)
uva7c
uva7c$keep_remove
```

@@

```{r}
uva8a <- EGAnet::UVA(data = data8a, cut.off = 0.3)
uva8a
uva8a$keep_remove
```

@@

```{r}
uva8b <- EGAnet::UVA(data = data8b, cut.off = 0.3)
uva8b
uva8b$keep_remove
```

@@

```{r}
uva9 <- EGAnet::UVA(data = data9, cut.off = 0.3)
uva9
uva9$keep_remove
```

@@

```{r}
uva10a <- EGAnet::UVA(data = data10a, cut.off = 0.3)
uva10a
uva10a$keep_remove
```

@@

```{r}
uva10b <- EGAnet::UVA(data = data10b, cut.off = 0.3)
uva10b
uva10b$keep_remove
```

@@

```{r}
uva10c <- EGAnet::UVA(data = data10c, cut.off = 0.3)
uva10c
uva10c$keep_remove
```

@@

```{r}
uva11a <- EGAnet::UVA(data = data11a, cut.off = 0.3)
uva11a
uva11a$keep_remove
```

@@

```{r}
uva11b <- EGAnet::UVA(data = data11b, cut.off = 0.3)
uva11b
uva11b$keep_remove
```

#### Summary

```{r}
rez_uva <- c(uva1a$keep_remove$remove,
  uva1b$keep_remove$remove,
  uva2$keep_remove$remove,
  uva3$keep_remove$remove,
  uva4$keep_remove$remove,
  uva5$keep_remove$remove,
  uva6$keep_remove$remove,
  uva7a$keep_remove$remove,
  uva7b$keep_remove$remove,
  uva7c$keep_remove$remove,
  uva8a$keep_remove$remove,
  uva8b$keep_remove$remove,
  uva9$keep_remove$remove,
  uva10a$keep_remove$remove,
  uva10b$keep_remove$remove,
  uva10c$keep_remove$remove,
  uva11a$keep_remove$remove,
  uva11b$keep_remove$remove)

sort(table(rez_uva), decreasing = TRUE) / length(rez_uva) 
```

@@

### Structure Refinement

Discarded the following items:
- Tickle: not present in the same dataset and consistently flagged as redundant in UVA analysis.
